A multi-dimensional extension of the Lightweight Temporal Compression method

### 2018-11-20 paper.tex
some change

\paragraph{Infinity vs Euclidean norms}
The average ratio between the compression ratios obtained
with the infinity and Euclidean norm is 1.08(1.04) for 2D data, and 1.20(1.14)
for 3D data. These ratios are lower than the theoretical values of
$\frac{4}{\pi}$ in 2D and $\frac{6}{\pi}$ in 3D, which are obtained for
random-uniform signals. Unsurprisingly, the infinity norm surpasses the
Euclidean norm in terms of resource consumption. Memory-wise, the
infinity norm requires a constant amount of 80~B, used to store the
intersection of n-balls. The Euclidean norm, however, uses up to 4.7~KB of memory
for the Long time-series in 3D with $\epsilon$=48.8~mg. More importantly,
the amount of required memory increases for longer time-series, and it also increases with larger
values of $\epsilon$. Similar observations are made for the processing
time, with values ranging from 0.2(0.4)~ms for the simplest time-series and
smallest $\epsilon$, to 41.3~ms for the most complex time-series and
largest~$\epsilon$.
%~ Figure~\ref{fig:memory} shows the memory consumption
%~ of the 3D Euclidean implementation for $\epsilon$=48.8~mg: peaks appear
%~ at the end of long compressed ranges where the signal was $\epsilon$-closed
%~ to the linear approximation.

\paragraph{2D vs 3D}
For a given $\epsilon$, the compression
ratios are always higher in 2D than in 3D. It makes sense since the
probability for the signal to deviate from a straight line
approximation is higher in 3D than it is in 2D. Besides, resource
consumption is higher in 3D than in 2D: for the infinity norm, 3D
consumes 1.4 times more memory than 2D (1.3(1.8) times on average for
Euclidean norm), and processing time is 1.2(1.4) longer (1.13(1.3) on
average for Euclidean norm).

@@

 Results are reported in Table~\ref{table:results-energy}. For a given
 $\epsilon$ and norm, the compression ratio is larger for walking than
 for running. The ratio of saved energy is relative to the reference
 current of 3.47~mA measured when Neblina transmits data without
 compression. In all cases, activating compression saves energy. The
 reduction in energy consumption behaves as the compression ratio: it
 increases with $\epsilon$,
it is higher for the infinity norm than for the Euclidean, and it is
higher for the walking activity than for running. For a realistic error
of $\epsilon$=9.8~mg, the ratio of saved energy with the infinity norm is
close to 20\% for the walking activity, which is substantial. We also
measured processing times of both infinity norm and Euclidean norm in
Neblina.The result is reported in Table~\ref{table:result-latency}.
In Neblina, the processing time of different data are similar in Infinity
norm. In Euclidean norm, the processing time is longer, and it uses more 
time when the data is more smooth.
\begin{table}[]
   \begin{subfigure}{\columnwidth}
   \centering
   \begin{tabular}{l|l|l|l|l|l|l}
   \hline
   \rowcolor{headcolor}
                          & \multicolumn{3}{c|}{Infinity} & \multicolumn{3}{c}{Euclidean} \\\hline
   $\epsilon$ (mg)             & 48.8       & 9.8      & 4.9       & 48.8      & 9.8       & 4.9    \\
   Max error (mg)              & 48.8     & 9.8        & 4.9      & 48.8   & 9.8   & 4.9  \\
   Compr.      ratio (\%)      & 88.9    & 66.4  & 45.5   & 87.6   & 63.3   & 37.2 \\
   Average (mA)                & 2.64     & 2.79   & 3.02   & 3.10    & 3.02    & 3.13  \\
   Saved energy (\%)              & 23.9    & 19.7  & 13.0  &  10.7   & 13.0   & 9.7\\
   \hline
   \end{tabular}
   \caption{Walking}
   \end{subfigure}
   \begin{subfigure}{\columnwidth}
   \centering
   \begin{tabular}{l|l|l|l|l|l|l}
   \hline
   \rowcolor{headcolor}

>>>>

\paragraph{Infinity vs Euclidean norms}
The average ratio between the compression ratios obtained
with the infinity and Euclidean norm is 1.04 for 2D data, and 1.14
for 3D data. These ratios are lower than the theoretical values of
$\frac{4}{\pi}$ in 2D and $\frac{6}{\pi}$ in 3D, which are obtained for
random-uniform signals. Unsurprisingly, the infinity norm surpasses the
Euclidean norm in terms of resource consumption. Memory-wise, the
infinity norm requires a constant amount of 80~B, used to store the
intersection of n-balls. The Euclidean norm, however, uses up to 4.7~KB of memory
for the Long time-series in 3D with $\epsilon$=48.8~mg. More importantly,
the amount of required memory increases for longer time-series, and it also increases with larger
values of $\epsilon$. Similar observations are made for the processing
time, with values ranging from 0.4~ms for the simplest time-series and
smallest $\epsilon$, to 41.3~ms for the most complex time-series and
largest~$\epsilon$.
%~ Figure~\ref{fig:memory} shows the memory consumption
%~ of the 3D Euclidean implementation for $\epsilon$=48.8~mg: peaks appear
%~ at the end of long compressed ranges where the signal was $\epsilon$-closed
%~ to the linear approximation.

\paragraph{2D vs 3D}
For a given $\epsilon$, the compression
ratios are always higher in 2D than in 3D. It makes sense since the
probability for the signal to deviate from a straight line
approximation is higher in 3D than it is in 2D. Besides, resource
consumption is higher in 3D than in 2D: for the infinity norm, 3D
consumes 1.4 times more memory than 2D (1.8 times on average for
Euclidean norm), and processing time is 1.4 longer (1.3 on
average for Euclidean norm).

@@

 Results are reported in Table~\ref{table:results-energy}. For a given
 $\epsilon$ and norm, the compression ratio is larger for walking than
 for running. The ratio of saved energy is relative to the reference
 current of 3.47~mA measured when Neblina transmits data without
 compression. In all cases, activating compression saves energy. The
 reduction in energy consumption behaves as the compression ratio: it
 increases with $\epsilon$,
it is higher for the infinity norm than for the Euclidean, and it is
higher for the walking activity than for running. For a realistic error
of $\epsilon$=9.8~mg, the ratio of saved energy with the infinity norm is
close to 20\% for the walking activity, which is substantial. We also
measured processing times of both infinity norm and Euclidean norm in
Neblina.The result is reported in Table~\ref{table:result-latency}.
In Neblina, the processing time of different data are similar in Infinity
norm. In Euclidean norm, the processing time is longer, and data with slight changes using more processing time with comparing result of walking data and running data.
\begin{table}[]
   \begin{subfigure}{\columnwidth}
   \centering
   \begin{tabular}{l|l|l|l|l|l|l}
   \hline
   \rowcolor{headcolor}
                          & \multicolumn{3}{c|}{Infinity} & \multicolumn{3}{c}{Euclidean} \\\hline
   $\epsilon$ (mg)             & 48.8       & 9.8      & 4.9       & 48.8      & 9.8       & 4.9    \\
   Max error (mg)              & 48.8     & 9.8        & 4.9      & 48.8   & 9.8   & 4.9  \\
   Compr.      ratio (\%)      & 88.9    & 66.4  & 45.5   & 87.6   & 63.3   & 37.2 \\
   Average (mA)                & 2.64     & 2.79   & 3.02   & 3.10    & 3.02    & 3.13  \\
   Saved energy (\%)              & 23.9    & 19.7  & 13.0  &  10.7   & 13.0   & 9.7\\
   \hline
   \end{tabular}
   \caption{Walking}
   \end{subfigure}
   \begin{subfigure}{\columnwidth}
   \centering
   \begin{tabular}{l|l|l|l|l|l|l}
   \hline
   \rowcolor{headcolor}
